Improving success ratio of EDF when taking into account the preemption cost in uniprocessor periodic systems

### 2013-10-11 python-simulation/paper-paedf/paper-paedf.tex
Renamed main to make place for a true main
Corrections by L.G.

\title{Improving schedulability rate of EDF when taking into account the preemption cost in uniprocessor periodic systems}
\author{Thomas Chapeaux}
\date{Summer 2013}
%opening
\sloppy
\begin{document}
\maketitle

@@

        A task $\tau_i$ generates jobs, denoted as the tuple $j_{i,j} = (a_{i, j}, d_{i,j}, c_{i,j})$ where :
        \begin{itemize}
            \item $j = \{1,2,...\}$ is an unique identifier for the job within $\tau_i$.
            \item $a_{i,j} = O_i + (j-1) \cdot T_i$ is the arrival time (or \emph{activation time}) of the job.
            \item $d_{i,j} = a_{i,j} + D_i$ is an absolute deadline at which the job must be completed.
            \item $c_{i,j} = C_i$ is the time it takes to complete the job (\emph{execution time}).
        \end{itemize}

        We also assume a discrete time, meaning that we consider that time passes one unit (sometimes called \emph{clock tick}) at a time. This means that the values listed above must be integers and that jobs will execute for whole units.\\

@@

        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (which are not synchronous). For synchronous systems, we assume without loss of generality that $O_i = 0 \; \forall i$.\\

@@

        \subsubsection{Feasibility Analysis}

@@

@@

    \subsection{Non-optimality}

@@

    \subsection{Anomalies}

@@

        \subsubsection{Deadline miss in transitive, not in periodic}

@@

@@

        \subsubsection{Dynamic dominate fixed-job}

@@

\section{PA-EDF: an extension of EDF for costly preemption}

>>>>

\title{Improving success ratio of EDF when taking into account the preemption cost in uniprocessor periodic systems}
\author{Thomas Chapeaux}
\date{Summer 2013}
%opening
\sloppy
\begin{document}
\maketitle

@@

        A task $\tau_i$ generates jobs, denoted as the tuple $j_{i,j} = (a_{i, j}, d_{i,j}, c_{i,j})$ where :
        \begin{itemize}
            \item $j = \{1,2,...\}$ is an unique identifier for the job within $\tau_i$.
            \item $a_{i,j} = O_i + (j-1) \cdot T_i$ is the arrival time (or \emph{activation time}) of the job.
            \item $d_{i,j} = a_{i,j} + D_i$ is an absolute deadline at which the job must be completed.
            \item $c_{i,j} = C_i$ is the time it takes to complete the job (\emph{execution time}).
        \end{itemize}
h
        We also assume a discrete time, meaning that we consider that time passes one unit (sometimes called \emph{clock tick}) at a time. This means that the values listed above must be integers and that jobs will execute for whole units.\\

@@

        Similarly, we differentiate between \textbf{synchronous system} (where $O_i = O_j \; \forall i,j$) and asynchronous systems (general case of unconstrained offset). For synchronous systems, we assume without loss of generality that $O_i = 0 \; \forall i$.\\

@@

        \subsubsection{Feasibility Analysis with no preemption cost}

        % TODO: add reference to cyclic idles times

@@

        % TODO : présenter différents modèles et justifier celui qu'on utilise

@@

    \subsection{Non-optimality of EDF}

@@

    \subsection{Scheduling anomalies w.r.t. the state of the art}

        % TODO: Introduction

@@

        \subsubsection{Deadline miss in transient, not in permanent}

@@

    % TODO: présenter les résultats sous forme de Lemmes

@@

        \subsubsection{Dynamic dominate fixed-job}
        % TODO: expliquer dynamic et fixed-priority job in the introduction

@@

\section{PA-EDF: an extension of EDF with preemption cost}

    %TODO : comparer avec les approches de limited preemptions (Marko Bertogna)
    %TODO : Introduire la notion d'alpha-horizon
    %TODO : essayer un algorithme "exhaustif" sur base de cet horizon
